The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-16 analysis/paper/paper.qmd
Update stopwords

The theses are available in PDF format with complex layouts typical to an urbanism project in which text and various types of graphics are combined. With the exception of a bilingual English-Spanish thesis, all thesis were written in English.

@@

Word-level tokenisation was applied with the `unnest_tokens()` function of the `tidytext` package. This was preferred over other tokenisers as it produced results that work seamlessly with other `tidyverse` tools used in the analysis.

@@

>>>>

The theses are available in PDF format with complex layouts typical to an urbanism project in which text and various types of graphics are combined.

@@

Word-level tokenisation was applied with the `unnest_tokens()` function of the `tidytext` package. This was preferred over other tokenisers as it produced results that work seamlessly with other `tidyverse` tools.

@@

emu_theses |> 
  find_meta_stopwords(convert_to_regex = FALSE)

emu_theses |> 
  urbanism_stopwords()
